Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-02-25 paper/paper.tex
work on nice mannik plot (needs more work) plus tune colors on boxplot Tested everything on bennet.
wrote some of the > shape, am debating about putting in the more complex analysis Tested everything on node23.

Along with our other shapes we have chosen to simulate both
equilateral and iscoscolese triangular pancake shapes, since these
offer in a way the simplest shapes that are geometrically more
complicated than our pill shapes.

Both triangle types show a similar oscillation pattern.  The
iscosolese exhibit regular oscillations characterized by one distinct
pole in the more accute angle of the three, and another 'pole' along
the opposite wall, peaking in the two more obtuse angles at the same
time.  The equilateral triangles settle very quickly into the same
pattern, where the choice of which is one pole corner is dependent
upon initial conditions.  As with the Mannik simulated shapes, there
is a critical small size below which the oscillations dampen out and
will not achieve a regular pattern.  Figure~\ref{box-triangle} shows
three plots of equilateral triangles.  The two smaller show the
largest that showed damped out behavoir and the smallest that
developed regular oscillations.  The larger shows the largest traingle
that we simulated, showing that at even very large sizes the behavoir
is consistent and stable.  Above the small size threshold, all
simulated triangles show regular patterns for as long as simulated
(roughly 800 seconds).

@@

\section{Our 'V' Shaped Cells}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-525-525-9900-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-550-550-9900-1500}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9900-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1400-1400-9900-1500}
\end{figure}

Our animations for this cell shape show a very interesting pattern.
The maxima oscillates from the right corner to the top corner, then
\emph{back to the right corner} then to the top corner again, then to
the left corner, then back to the top, then to the left, then to the
top again, then back to the right side.

@@

Contour plot frames from the animations show the second maxima in the
lower left corner (immediately following the one in the upper middle
corner) will reside for a bit longer than the left corner maxima
preceding it.  These longer residing maxima will then be followed by a
switch, to the right corner, with a short, less intensive maxima
traveling through the center.  The MinE shows the same pattern. The
MinE that was just concentrated on the left corner during the first
maxima, after releasing the MinD from the membrane there, diffuses up
and attaches to the MinD on the upper corner membrane and begins to
release it.  During this process the MinE starts at the edges and
moves in towards the center of the maxima.  The center of the cup is a
little further away so it attaches to these outer ridges first and
then moves in.  After it eats at the corners and starts moving in the
MinD eventually travels back to set up a maxima in the left corner.
Watching the cytoplasmic MinE, something very interesting: It as well
maximizes twice in the left corner, but during the MinD's first maxima
in the left corner, the MinD has a maxima in the upper corner, and
during the MinD's second left maxima, the MinE travels to the right
corner and has a maxima there.  At the same time (during the second
MinD left corner maxima), there is a large amount of cytoplasmic
MinD:ATP on the right side.  The MinE does this becuase during the
first MinD left corner maxima, the MinE has just come off a maxima in
the right corner.  So it diffuses up to the upper corner and sets up
there.  During the second MinD left corner maxima, the MinE has just
come off the upper corner maxima.  It will diffuse into the right
corner and left corner.  In the left corner it interacts with the MinD
bound to the membrane there.  In the right corner it sits and
eventually diffuses away, but at a somewhat slow pace.  \fixme{An idea
  is that once the MinD travels back from the left corner after its
  second maxima there, it is not able tot set up a maxima in the upper
  corner as easily, since there is left over MinE there, which has
  just traveled from the right corner.  The problem with this is that
  the MinE doesn't seem to be maximized in the upper corner when the
  MinD is traveling back up from the left.}  The other idea is simply
that because the minE is traveling all the way from the right corner,
the longer time it takes to get there simply means that it all
concentrates on the left, leaving the upp and right side completely
open for the build up of MinD.  \fixme{Still dont quite get it but
  take a look at the other simulations and come back.} Actually, you
can see this effect very slightly watching the 98 shape, between the
center cap and the right corner.

>>>>

Along with our other shapes we have chosen to simulate both
equilateral and iscoscolese triangular flattened shapes, since these
offer in a way the simplest shapes that are geometrically more
complicated than our pills.

Both triangle types show a similar oscillation pattern.  The
iscosolese exhibit regular oscillations characterized by one distinct
pole in the more accute angle of the three, and another 'pole' along
the opposite wall, peaking in the two more obtuse angles at the same
time.  The equilateral triangles settle very quickly into the same
pattern, where the choice of which is one pole corner is dependent
upon initial conditions.  As with the Mannik simulated shapes, there
is a critical small size below which the oscillations dampen out and
will not achieve a regular pattern.  Figure~\ref{box-triangle} shows
two plots of equilateral triangles.  The two smaller show the
largest that showed damped out behavoir and the smallest that
developed regular oscillations.  The larger shows the largest traingle
that we simulated, showing that at even very large sizes the behavoir
is consistent and stable.  Above the small size threshold, all
simulated triangles show regular patterns for as long as simulated
(roughly 800 seconds).

@@

\section{Our '\textgreater' Shaped Cells}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-525-525-9900-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-550-550-9900-1500}
  \label{>-box}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9900-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1400-1400-9900-1500}
  \label{>-box2}
\end{figure}

We have simulated a flattened '>' shape that shows an interesting size
dependent pattern (seen in Figures~\ref{>-box}~and~\ref{>-box2}).
When the shape is small enough that the distance from the apex tip to
the opposite curve is less than our stability limit, a simple, two
pole oscillation pattern develops and is sustained (where the two
poles are on opposite leftward corners of the cell).  When the cell is
increased in size, so that this distance measures approximately equal
to our stability value, the cell develops a double oscillation in
time, where the maxima oscillates from the lower corner to the
rightward apex, then \emph{back to the lower corner} then to the apex
again, then to the upper corner, then back to the apex, then to the
upper corner, then to the apex again, then back to the lower corner,
and continues this pattern indefinately.  Figure~\ref{>-box} shows the
smaller size, which oscillates simply, and an intermediate size, which
shows a pattern for which one out of three spikes in the regular
oscillation is less significant.  This second pattern seems to be a
precursor to the double oscillation seen in Figure~\ref{>-box2}.  The
second plot shown in Figure~\ref{>-box2} shows a slighlty larger cell,
for which the distance measured is larger than our stability limit
distance.  This shows a very random pattern.

@@

Contour plot frames from the animations show the second maxima in the
lower left corner (immediately following the one in the upper middle
corner) will reside for a bit longer than the left corner maxima
preceding it.  These longer residing maxima will then be followed by a
switch, to the right corner, with a short, less intensive maxima
traveling through the center.  The MinE shows the same pattern. The
MinE that was just concentrated on the left corner during the first
maxima, after releasing the MinD from the membrane there, diffuses up
and attaches to the MinD on the upper corner membrane and begins to
release it.  During this process the MinE starts at the edges and
moves in towards the center of the maxima.  The center of the cup is a
little further away so it attaches to these outer ridges first and
then moves in.  After it eats at the corners and starts moving in the
MinD eventually travels back to set up a maxima in the left corner.
Watching the cytoplasmic MinE, something very interesting: It as well
maximizes twice in the left corner, but during the MinD's first maxima
in the left corner, the MinE has a maxima in the upper corner, and
during the MinD's second left maxima, the MinE travels to the right
corner and has a maxima there.  At the same time (during the second
MinD left corner maxima), there is a large amount of cytoplasmic
MinD:ATP on the right side.  The MinE does this becuase during the
first MinD left corner maxima, the MinE has just come off a maxima in
the right corner.  So it diffuses up to the upper corner and sets up
there.  During the second MinD left corner maxima, the MinE has just
come off the upper corner maxima.  It will diffuse into the right
corner and left corner.  In the left corner it interacts with the MinD
bound to the membrane there.  In the right corner it sits and
eventually diffuses away, but at a somewhat slow pace.  \fixme{An idea
  is that once the MinD travels back from the left corner after its
  second maxima there, it is not able tot set up a maxima in the upper
  corner as easily, since there is left over MinE there, which has
  just traveled from the right corner.  The problem with this is that
  the MinE doesn't seem to be maximized in the upper corner when the
  MinD is traveling back up from the left.}  The other idea is simply
that because the minE is traveling all the way from the right corner,
the longer time it takes to get there simply means that it all
concentrates on the left, leaving the upp and right side completely
open for the build up of MinD.  \fixme{Still dont quite get it but
  take a look at the other simulations and come back.} Actually, you
can see this effect very slightly watching the 98 shape, between the
center cap and the right corner.
